FictionEro - Affective Impact of Fiction

### 2025-06-10 study1/analysis/1_cleaning.qmd
updated data scripts and data

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "means") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT - Visual")
```

>>>>

  modelbased::estimate_means(m, by=c("AI_Knowledge")) |>
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=Mean)) +
  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT - Visual")
```

### 2025-06-10 study1/analysis/2_emotions.qmd
updated data scripts and data

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

@@

@@

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / (Condition * Screen_Size) + (Relevance | Participant) + (1|Item),
                      data=standardize(df, select="Screen_Size"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
  f <- paste0(outcome, " ~ Sex / (Condition * ", moderator, ") + (Condition | Participant) + (1|Item)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data=filter(df, Relevance == "Relevant"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

@@

```{r}
  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m_enticement <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + 
                                   (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- Effect becomes larger, more significant and goes in both directions for both genders -->

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m_valence <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

pred1 <- rbind(
  marginaleffects::predictions(m_arousal, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  marginaleffects::predictions(m_enticement, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  marginaleffects::predictions(m_valence, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

>>>>

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

@@

<!-- Note: The model did not converge when adding Relevance and Condition as random slopes for Item. -->

@@

*Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli.

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance / Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli.

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance / Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- *Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli. -->

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / (Condition * Screen_Size) + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=standardize(df, select="Screen_Size"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- Note. Not enough contrasts to add relevance and condition as random slopes for items -->
```{r}
test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
  f <- paste0(outcome, " ~ Sex / (Condition * ", moderator, ") + (Condition | Participant) + (1|Item)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data=filter(df, Relevance == "Relevant"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

@@

<!-- *Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli. -->

```{r}
  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note*. Model adding Relevance and Condition as random slopes for each stimuli converged

```{r}
m_enticement <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + 
                                   (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * SexualActivity_num) + (Condition | Participant) + ((Relevance/Condition)|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- Effect becomes larger, more significant and goes in both directions for both genders -->
*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
```{r}
m_valence <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

pred1 <- 
  rbind(
  modelbased::estimate_means(m_Arousal, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition") |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)
